Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-26 mplr-2021/main.tex
cosmetics

\paragraph*{Further types}
Similar approaches could be conceived for indexed types, polymorphic types, dependent
types, etc. However, at present we believe incorporating these
features in a tool to be of limited value because they are not widely used in DefinitelyTyped (see
Table~\ref{tab:dts-parse-stats}).

>>>>

\paragraph*{Further types}
Similar approaches could be conceived for indexed types, polymorphic types, dependent
types, etc. At present we believe incorporating these
features in a tool to be of limited value because they are not widely used in DefinitelyTyped (see
Table~\ref{tab:dts-parse-stats}).
